---
title: "Biomarker 113 Analytic Report"
author: 
- Timothy Tsai, MPH
date: "`r Sys.Date()`"
mainfont: TeX Gyre Pagella
output: 
  memor::pdf_memo:
    use_profile: false
    logo: "tree-template-logo.pdf"
    logo_height: 2in
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

Biomarker A113 is a γ-β secretase inhibitor which is thought to downregulate the examplin-C enzyme, a necessary component for cell formation in the ossmodula.  Decreased cell formation in the ossmodula is associated with increased rates of fracture and decreased mobility in several large, population-based studies.  Biomarker A113 is a potential candidate for intervention however, there have been relatively few studies of A113 in humans.

In this study, we collected morning fasting blood samples from ______ participants aged ____ to ____.  We conducted A113 assays by multispectral peripheral absorptiometry using a 12 array micropanel (AssayGen, Salem, MA).

## Statistical Analysis

```{r cars}
summary(cars)
```

# Results

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
