---
title: |
  | Biomarker 113 Analytic Report
  | for R/Medicine 2019
author: 
- Timothy Tsai, MPH
date: "`r Sys.Date()`"
mainfont: TeX Gyre Pagella
output: 
  memor::pdf_memo:
    use_profile: false
    logo: "tree-template-logo.pdf"
    logo_height: 2in
    toc: true
---

```{r setup, include=FALSE}
library(knitr)
library(kableExtra)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
options(knitr.table.format = "latex")
opts_knit$set(root.dir = '../..')
```

```{r import, echo=F}
source("data/clinical_data.R")
source("report/Biomarker A113 Analysis/01_create_datasets.R")
source("report/Biomarker A113 Analysis/tables.R")
source("report/Biomarker A113 Analysis/figures.R")
source("report/Biomarker A113 Analysis/models.R")
```

```{r, echo = FALSE}
n_pts <- clinic_lab_data_analytic %>% tally() %>% pull()
age_range <- range(clinic_lab_data_analytic$age)
```

# Introduction

Biomarker A113 is a γ-β secretase inhibitor which is thought to downregulate the examplin-C enzyme, a necessary component for cell formation in the ossmodula.  Decreased cell formation in the ossmodula is associated with increased rates of fracture and decreased mobility in several large, population-based studies.  Biomarker A113 is a potential candidate for intervention however, there have been relatively few studies of A113 in humans.

In this study, we collected morning fasting blood samples from `r n_pts` participants aged `r age_range[1]` to `r age_range[2]` y.  We conducted A113 assays by multispectral peripheral absorptiometry using a 12 array micropanel (AssayGen, Salem, MA).

# Results

## Descriptive Statistics

```{r, echo = FALSE}
kable(clinic_lab_data_summary_table, booktabs = TRUE, col.names = c("", "Female", "Male"), 
      align = c("l", "c", "c"),
      caption = "Descriptive Statistics") %>% 
  kable_styling(latex_options = "hold_position")
```

## Exploratory Analyses

```{r, echo = FALSE}
histograms
```

```{r, echo = FALSE}
x_age_plot
```

```{r, echo = FALSE}
a_age_plot
```

## Statistical Analysis
modeling  
regression output

```{r, echo=FALSE}
kable(models_out, booktabs = TRUE) %>% 
  pack_rows("Unadjusted", 1, 2) %>% 
  pack_rows("Sex Adjusted", 3, 5) %>% 
  pack_rows("Fully Adjusted", 6, 10)
```
